\uppercase{Fabric-Elasticity Relationships of Tibial Trabecular Bone are Similar in Osteogenesis Imperfecta and Healthy Individuals}

### 2021-06-28 12_SBMS_Presentation/SBMS_Simon_et_al.tex
Second article co-authors revision

\begin{frame}
	\frametitle{Fit to Model}
	\begin{columns}
		\column{.5\textwidth}
		Stiffness tensor $\mathbb{S}$
		\begin{itemize}
			\item \si{\micro}FE homogenization
			\item Transformation and projection
		\end{itemize}\vspace{1em}
		Linear Regression
		\begin{itemize}
			\item Linear mixed-effects model\\
			\item Fit to Zysset-Curnier model\\
			$\mathbb{S}$ \textasciitilde \textcolor{blue}{$\lambda_{0}$}, \textcolor{blue}{$\lambda_{0}$'}, \textcolor{blue}{$\mu_{0}$}, $m_{i}m_{j}^{\textcolor{red}{k}}$, BV/TV$^{\textcolor{red}{l}}$
			\item Log space for \textcolor{red}{$k$} and \textcolor{red}{$l$}
			\item $R_{adj}^{2}$ and NE for fit quality
		\end{itemize}

@@

@@

	Regression conditions:
	\begin{itemize}
		\item Matching allow to fit over same range
		\item Identical $k$ and $l$ for healthy and OI comparison
	\end{itemize}

@@

\begin{frame}
	\frametitle{BV/TV and DA Matching - Tissue BMD (tBMD)}
	\fontsize{10pt}{10pt}\selectfont
	\begin{columns}
		\column{0.5\textwidth}

@@

\subsection{Comparison with Other Resolutions}

\begin{frame}
	\frametitle{Comparison with Other Resolutions}
	\fontsize{10pt}{10pt}\selectfont

	\begin{table}[]
		\centering
		\caption{Summary of studies compared\vspace{-1em}}
		\label{Table4}\resizebox{1.\linewidth}{!}{
			\begin{tabular}{lccc}
				\toprule
				Study & Scanned site & Scan & Resolution \\
				\midrule

				\cite{p13} & Multiple sites & \si{\micro}CT & 18\si{\micro}m $\rightarrow$ 36\si{\micro}m \\

				\cite{p7} & Proximal femur & \si{\micro}CT & 18\si{\micro}m $\rightarrow$ 36\si{\micro}m \\

				Present study & Distal tibia & HR-pQCT & 61\si{\micro}m \\
				\bottomrule
		\end{tabular}}
	\end{table}

	\begin{columns}[t]
		\column{0.5\textwidth}
		Higher DA
		\begin{itemize}
			\item Distal tibia vs proximal femur
		\end{itemize}

		\vspace{7pt}

		Lower stiffness constants ($\lambda_0$, $\lambda_0'$, $\mu_0$)
		\begin{itemize}
			\item 61\si{\micro}m vs 36\si{\micro}m
		\end{itemize}

		\vspace{7pt}

		Lower fit quality ($R^2_{adj}$ and NE)
		\begin{itemize}
			\item 61\si{\micro}m vs 36\si{\micro}m
		\end{itemize}

		\column{0.5\textwidth}
		Higher $k$
		\begin{itemize}
			\item Higher weight of BV/TV
		\end{itemize}

		\vspace{7pt}

		Similar $l$
		\begin{itemize}
			\item Similar weight of DA
		\end{itemize}

>>>>

\begin{frame}
	\frametitle{Fit to Model}
	\begin{columns}
		\column{.5\textwidth}
		Stiffness tensor $\mathbb{S}$
		\begin{itemize}
			\item \si{\micro}FE homogenization
			\item Transformation and projection
		\end{itemize}\vspace{1em}
		Multiple Linear Regression
		\begin{itemize}
			\item Fit to Zysset-Curnier model\\
			$\mathbb{S}$ \textasciitilde \textcolor{blue}{$\lambda_{0}$}, \textcolor{blue}{$\lambda_{0}$'}, \textcolor{blue}{$\mu_{0}$}, $m_{i}^{\textcolor{red}{k}}m_{j}^{\textcolor{red}{k}}$, BV/TV$^{\textcolor{red}{l}}$
			\item Log space for \textcolor{red}{$k$} and \textcolor{red}{$l$}
			\item $R_{adj}^{2}$ and NE for fit quality
		\end{itemize}

@@

		\vspace{17.5pt}

		Tissue BMD (tBMD)
		\begin{itemize}
			\item BV/TV and DA matching
		\end{itemize}

@@

	Regression conditions:
	\begin{itemize}
		\item Matching allow to fit over same range
		\item Identical $k$ and $l$ for stiffness comparison
	\end{itemize}

@@

\begin{frame}[noframenumbering]
	\frametitle{Linear Regression - BV/TV and DA Matching}

	Regression conditions:
	\begin{itemize}
		\item Matching allow to fit over same range
		\item Identical $k$ and $l$ for stiffness comparison
	\end{itemize}

	\begin{table}[]
		\centering
		\caption{Summary of BV/TV and DA matched data set linear regression\vspace{-1em}}
		\label{Table4}\resizebox{1.\linewidth}{!}{
			\begin{tabular}{cccccccc}
				\toprule
				Data set & $\lambda_0$ & $\lambda_0'$ & $\mu_0$ & $k$ & $l$ & $R^2_{adj}$ & NE (\%) \\
				\midrule
				Grouped & 4626 [3892-5494] & 2695 [2472-2937] & 3541 [3246-3862] & 1.91 [1.86-1.95] & 0.95 [0.93-0.97] & 0.936 & 19 $\pm$ 9\\

				Healthy & 4318 [\hl{3844-4851}] & 2685 [\hl{2533-2845}] & 3512 [\hl{3306-3731}] & \textcolor{gray}{1.91} & \textcolor{gray}{0.95} & 0.835 & 21 $\pm$ 10\\

				OI & 4983 [\hl{4345-5716}] & 2727 [\hl{2547-2921}] & 3600 [\hl{3355-3863}] & \textcolor{gray}{1.91} & \textcolor{gray}{0.95} & 0.860 & 20 $\pm$ 10\\
				\bottomrule
		\end{tabular}}
	\end{table}

\begin{frame}
	\frametitle{BV/TV and DA Matching - tBMD}
	\fontsize{10pt}{10pt}\selectfont
	\begin{columns}
		\column{0.5\textwidth}

@@

%\subsection{Comparison with Other Resolutions}
%
%\begin{frame}
%	\frametitle{Comparison with Other Resolutions}
%	\fontsize{10pt}{10pt}\selectfont
%	
%	\begin{table}[]
%		\centering
%		\caption{Summary of studies compared\vspace{-1em}}
%		\label{Table4}\resizebox{1.\linewidth}{!}{
%			\begin{tabular}{lccc}
%				\toprule
%				Study & Scanned site & Scan & Resolution \\
%				\midrule
%				
%				\cite{p13} & Multiple sites & \si{\micro}CT & 18\si{\micro}m $\rightarrow$ 36\si{\micro}m \\
%				
%				\cite{p7} & Proximal femur & \si{\micro}CT & 18\si{\micro}m $\rightarrow$ 36\si{\micro}m \\
%				
%				Present study & Distal tibia & HR-pQCT & 61\si{\micro}m \\
%				\bottomrule
%		\end{tabular}}
%	\end{table}
%
%	\vfill
%
%	\begin{columns}[t]
%		\column{0.5\textwidth}
%		Higher DA
%		\begin{itemize}
%			\item Distal tibia vs proximal femur
%		\end{itemize}
%	
%		\vspace{7pt}
%		
%		Lower stiffness constants ($\lambda_0$, $\lambda_0'$, $\mu_0$)
%		\begin{itemize}
%			\item 61\si{\micro}m vs 36\si{\micro}m
%		\end{itemize}
%	
%		\vspace{7pt}
%		
%		Lower fit quality ($R^2_{adj}$ and NE)
%		\begin{itemize}
%			\item 61\si{\micro}m vs 36\si{\micro}m
%		\end{itemize}
%	
%		\column{0.5\textwidth}
%		Higher $k$
%		\begin{itemize}
%			\item Higher weight of BV/TV
%		\end{itemize}
%	
%		\vspace{7pt}
%		
%		Similar $l$
%		\begin{itemize}
%			\item Similar weight of DA
%		\end{itemize}
%	
%	\end{columns}
%\end{frame}
